Data Exploration: IUCN and AquaMaps

### 2016-03-11 data_explore/data_explore.Rmd
created mapping chunk for iucn gap and 10+ species cells

>>>>

``` {r plot_spp_iucn_gaps_tenplus, eval = TRUE, echo = FALSE}

iucn_gap10     <- read_csv(file.path(dir_data, 'iucn_gaps_tenplus.csv'))
iucn_gap10_spp <- unique(iucn_gap10[iucn_gap10$sciname %in% spp_list$sciname, ])

iucn_gapmaps <- sample_n(iucn_gap10_spp %>% filter(cat == 'gap'), 10)
iucn_10maps  <- sample_n(iucn_gap10_spp %>% filter(cat != 'gap'), 10)

if(!exists('iucn_spp_cells')) 
  iucn_spp_cells <- read_csv(file.path(dir_anx, 'explore_am_v_iucn/iucn_spp_cells_2015.csv'))

for (spp in iucn_gapmaps$sciname) { # i = 1
  spp_plot <- plot_rangemap(spp)
  spp_solo <- spp_list %>% filter(sciname == spp)
  spp_plot <- spp_plot +
    labs(title = sprintf('%s: %s', spp, spp_solo$spp_group_text))

  print(spp_plot)
}

```
***
